Transactional Memory Concurrency Verification with Landslide

### 2018-03-13 htm/paper.tex
minor fixes

MCs may instrument programs to introduce thread switches at varying granularity, which affects the number of operations $n$.
%The number of operations depends on how finely-grained the MC instruments the program to introduce thread switches.
Some target distributed systems, instrumenting only message-passing events \cite{modist};
some run multithreaded programs natively, instrumenting only the pthread API for performance \cite{dbug-ssv};
and some insert compiler instrumentation on statically-identified memory accesses \cite{chess,inspect}.
Landslide traces every memory access through the use of a simulated environment \cite{bochs},
which is important for identifying data races to use as new preemption points \cite{fasttrack,djit,quicksand},
as well as for identifying when a memory conflict may cause transaction aborts.
With regard to checking for bugs,
the ``model'' the name refers to being checked may be
an external formal specification,
the program's own internal consistency checks,
or a set of expected properties encoded in the tool itself.
Landslide uses the latter two cases, checking for assertion failures
as well as deadlocks, use-after-frees, and segfaults.

@@

\begin{theorem}[Atomicity of Transactions]
	\label{thm:atom}
	For any state space $U$ of a transactionally-concurrent program,
	an equivalent state space exists in which all transactions are either executed atomically or aborted immediately.
\end{theorem}

\begin{proof}
	For every $I \in U$ with $\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b},$ $\tjjat{\dots},\tkkat{\dots},\tiiat{\beta_{b+1}} \in I$,
	apply Lemma~\ref{lem:equiv} to obtain an equivalent interleaving $I'$ satisfying the theorem condition.
	The resulting $U'$ can then be MCed without simulating HTM rollbacks.
\end{proof}

>>>>

MCs may instrument programs to introduce thread switches at varying granularity, which affects the number of operations $n$.
%The number of operations depends on how finely-grained the MC instruments the program to introduce thread switches.
Some target distributed systems, instrumenting only message-passing events \cite{modist};
some run multithreaded programs natively, instrumenting only the pthread API for performance \cite{dbug-ssv};
and some insert compiler instrumentation on statically-identified memory accesses \cite{chess,inspect}.
Landslide traces every memory access through the use of a simulated environment \cite{bochs},
which is important for identifying data races to use as new preemption points \cite{fasttrack,djit,quicksand},
as well as for identifying when a memory conflict may cause transaction aborts.
With regard to checking for bugs,
the ``model'' the name refers to being checked may be
an external formal specification,
the program's own internal consistency checks,
or a set of expected properties encoded in the tool itself.
Landslide uses the latter two cases, checking for assertion failures
as well as deadlocks, use-after-frees, and segfaults.
For this work we also detect use of {\tt xend} outside of a transaction as a bug.

@@

\begin{theorem}[Atomicity of Transactions]
	\label{thm:atom}
	For any state space $S$ of a transactionally-concurrent program,
	an equivalent state space exists in which all transactions are either executed atomically or aborted immediately.
\end{theorem}

\begin{proof}
	For every $I \in S$ with $\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b},$ $\tjjat{\dots},\tkkat{\dots},\tiiat{\beta_{b+1}} \in I$,
	apply Lemma~\ref{lem:equiv} to obtain an equivalent interleaving $I'$ satisfying the theorem condition.
	The resulting $S'$ can then be MCed without ever simulating HTM rollbacks.
\end{proof}
